Results

### 2023-04-24 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
alignment of table 1

\begin{lltable}

\begin{longtable}{rccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, corrugator activity, and levator activity for each condition.}\\
\toprule
 & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:TabDescr} continued}}\\
\toprule
 & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
\midrule
\endhead
$View_{neu}$ & 26.6 ± 39.1 & 18.1 ± 27.4 &  & 0.04 ± 6.99 & 0.09 ± 1.84\\
$View_{neg}$ & 187.8 ± 87.3 & 49.4 ± 62.3 &  & 1.03 ± 7.21 & 0.58 ± 3.2\\
Distraction & 158.1 ± 92.5 & 208.5 ± 96.1 & 216.6 ± 93.2 & 0 ± 7.67 & -0.05 ± 1.16\\
Distancing & 164 ± 87.2 & 189.8 ± 92.3 & 214.8 ± 78.6 & 0.25 ± 1.92 & 0.01 ± 1\\
Suppression & 168.6 ± 95.8 & 158.3 ± 99.5 & 229.3 ± 95 & 0.07 ± 3.78 & -0.03 ± 0.92\\
\bottomrule
\end{longtable}

\end{lltable}

>>>>

\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, corrugator activity, and levator activity for each condition.}

\begin{tabular}{p{2.5cm}p{2.5cm}p{2.5cm}p{2.5cm}p{2.5cm}p{2.5cm}}
\toprule
 & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
\midrule
$View_{neu}$ & 26.6 ± 39.1 & 18.1 ± 27.4 &  & 0.04 ± 6.99 & 0.09 ± 1.84\\
$View_{neg}$ & 187.8 ± 87.3 & 49.4 ± 62.3 &  & 1.03 ± 7.21 & 0.58 ± 3.2\\
Distraction & 158.1 ± 92.5 & 208.5 ± 96.1 & 216.6 ± 93.2 & 0 ± 7.67 & -0.05 ± 1.16\\
Distancing & 164 ± 87.2 & 189.8 ± 92.3 & 214.8 ± 78.6 & 0.25 ± 1.92 & 0.01 ± 1\\
Suppression & 168.6 ± 95.8 & 158.3 ± 99.5 & 229.3 ± 95 & 0.07 ± 3.78 & -0.03 ± 0.92\\
\bottomrule
\end{tabular}

### 2023-04-24 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
alignment of table 1

```{r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  df.descr,
  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, corrugator activity, and levator activity for each condition.",
  escape = FALSE,
  placement = "H",
  align = c("r","c","c","c","c","c"),
  landscape = TRUE)
```

>>>>

```{r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  df.descr,
  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, corrugator activity, and levator activity for each condition.",
  escape = FALSE,
  placement = "H",
  align = c("p{2.5cm}", rep("p{2.5cm}", ncol(df.descr))),
  landscape = FALSE)
```
